Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-05-28 Paper.tex
abstract shortened

\title{Relational Presentation Using Semantic Closeness\\Spatial Narrative for
  Mathematical Content}
\author{Naomi Pentrel, Michael Kohlhase}
\institute{Jacobs University Bremen}
%----------------------------------------------------------------------------------------
% Macros
%----------------------------------------------------------------------------------------

@@

 \begin{abstract}
Visualization of knowledge is important to foster learning. Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts. To optimize the visualization of information and its interdependencies, a way to present information without loosing context is necessary. The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.

Taking the typical Mathematics lecture as an example, it is often the case that students have different backgrounds. Some might have learned linear algebra while other have not yet. Additionally, especially towards the end of the semester, students often have difficulties remembering earlier topics. When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up.

The OMDoc (OpenMathematical Documents) format is a content markup scheme for mathematical documents. Using OMDoc, the proposed system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on by taking a small detour through those topics, should they need to refresh their memories. Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning. This approach to presenting learning materials changes how we interact with course material which will allow students to learn better. Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.
\end{abstract}

>>>>

\title{Relational Presentations Using Semantic Closeness\\Spatial Narrative for
  Mathematical Content}
\author{Naomi Pentrel, Michael Kohlhase}
\institute{Jacobs University Bremen}
%----------------------------------------------------------------------------------------
% Macros
%----------------------------------------------------------------------------------------

@@

\begin{abstract}
Visualization of knowledge is important to foster learning. Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts. Taking the typical Mathematics lecture as an example, it is often the case that students come from different backgrounds. When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up on topics they have not learned. To optimize the visualization of information and its interdependencies, a way to present information without loosing context is therefore necessary. The following research takes an existing annotated corpus and presents its contents while allowing students to see dependencies between topics and encouraging them to explore related mathematical concepts. Thus students can interactively learn the concepts the current topic depends on by taking small detours through those topics, should they need to refresh their memories. This approach to presenting learning materials changes how we interact with course materials and it is ultimately applicable to almost all areas in which knowledge needs to be transferred.
\end{abstract}
